### 2024-06-10 slides/data.tex
presentation upload
before presentation

    \frametitle{Data} % Title
    \framesubtitle{}  % Subtitle
    \rmfamily % Font

    \begin{wideitemize}
        \item \textcolor{fgre}{USBLS's LAUS Database} \(\to\) county-level unemployment statistics (1990-2023)
        \item \textcolor{fgre}{US Census Bureau's Population Estimates Program (PEP)} \(\to\) county-level population and demographics (1969-2020)
        \item \textcolor{fgre}{USDOL's Changes in Basic Minimum Wages} (1968-2023)
        \item \textcolor{fgre}{Horwitz et al. (2020)} \(\to\) Prescription Drug Monitoring Programs (1990-2019)
    \end{wideitemize}

@@

    \begin{wideitemize}
        \item Unemployment, PDMPs, Minimum Wage rates and demographics for counties of 50 States + DC, 1998-2019
    \end{wideitemize}

>>>>

    \frametitle{Data I} % Title
    \framesubtitle{}  % Subtitle
    \rmfamily % Font

    \begin{wideitemize}
        \item \textcolor{fgre}{US Bureau of Labor Statistics (BLS)}  
        \vspace{9pt}
        \begin{wideitemize}
            \item[\textcolor{fgre}{\textbullet}] \textcolor{fgre}{LAUS Database} \(\to\) County-level labor market statistics (1990-2023)
            \item[\textcolor{fgre}{\textbullet}] \textcolor{fgre}{OEWS Database} \(\to\) National industry-specific occupations and wages statistics (1997-2023) % Occupational Employment and Wage Statistics
        \end{wideitemize}
        \item \textcolor{fgre}{Eckert et al. (2020)} \(\to\) County-level industry-specific employment (1975-2016) 
        \item \textcolor{fgre}{USDOL's Changes in Basic Minimum Wages} (1968-2023)
        \item \textcolor{fgre}{US Census Bureau's Population Estimates Program (PEP)} \(\to\) County-level population and demographics (1969-2020)
        \item \textcolor{fgre}{DEA's ARCOS} \(\to\) Opioid distribution data (2006-2014)
    \end{wideitemize}

    \frametitle{Data II} % Title
    \framesubtitle{}  % Subtitle
    \rmfamily % Font

    \begin{wideitemize}
        \item \textcolor{fgre}{Horwitz et al. (2020)} \(\to\) Prescription Drug Monitoring Programs (1990-2019)
        \item \textcolor{fgre}{Centers for Disease Control (CDC)} 
        \vspace{9pt}
        \begin{wideitemize}
            \item[\textcolor{fgre}{\textbullet}] \textcolor{fgre}{National Vital Statistics System} \(\to\) Total drug poisoning mortality by county (2003-2021)
            \item[\textcolor{fgre}{\textbullet}] \textcolor{fgre}{Multiple Cause of Death} \(\to\) Overdose deaths at the state-year level, for different drugs (1999-2020)
        \end{wideitemize}

    \end{wideitemize}

@@

    \begin{wideitemize}
        \item Unemployment, PDMPs, Minimum Wage rates and demographics for counties of 50 States + DC, 1998-2019
        \item County-level industry-weighted wage distribution and death mortality for counties of 50 States + DC, 2003-2016
    \end{wideitemize}

### 2024-06-10 slides/estimation.tex
before presentation

    \begin{wideitemize}
        \item Individual-level event study for different minimum wage quantiles: \textcolor{fgre}{Arkhangelsky, Yanagimoto and Zohar (in progress)}
    \end{wideitemize}

    \begin{equation*}
        y_{ct} = \alpha_c + \lambda_t + \sum_{k\geq h}\tau_{ck} + \beta X_{ct} + \nu_{ct}
    \end{equation*}
    with 
    \vspace{9pt}
    \begin{wideitemize}
        \item[\textcolor{fblu}{\textbullet}] \(\textcolor{fblu}{c}\): county, \(\textcolor{fblu}{t}\): time (year-month), \(\textcolor{fblu}{k = t - z_c}\): time difference from PDMP implementation year in county \(\textcolor{fblu}{c}\), \(\textcolor{fblu}{z_c}\)
        \item[\textcolor{fblu}{\textbullet}] \(\textcolor{fblu}{y_{ct}}\): labor market outcome, \(\textcolor{fblu}{X_{ct}}\): demographic covariates, \(\textcolor{fblu}{\nu_{ct}}\): idiosyncratic shock 
    \end{wideitemize}
    \vspace{9pt}
    State-level changes must be exogenous at the county level for \textcolor{fblu}{identification} and no anticipation up to \(\textcolor{fblu}{h}\) periods

@@

    \begin{center}
        \includegraphics[scale=0.4]{mop10_unemp_rate.png}
    \end{center}

    \hyperlink{perc_comparison_1}{\beamerbutton{Percentiles comparison}}
    \hyperlink{ta_1}{\beamerbutton{Time average}}

@@

    \begin{center}
        \includegraphics[scale=0.4]{mop10_emp_rate.png}
    \end{center}

    \hyperlink{perc_comparison_2}{\beamerbutton{Percentiles comparison}}
    \hyperlink{ta_2}{\beamerbutton{Time average}}

@@

    \begin{center}
        \includegraphics[scale=0.4]{mop10_lab_force_rate.png}
    \end{center}

    \hyperlink{perc_comparison_3}{\beamerbutton{Percentiles comparison}}
    \hyperlink{ta_3}{\beamerbutton{Time average}}

>>>>

    \begin{wideitemize}
        \item Individual-level event study for different minimum wage quantiles: \textcolor{fgre}{Arkhangelsky, Yanagimoto and Zohar (2024)}
    \end{wideitemize}

    \begin{equation*}
        y_{ct} = \alpha_c + \lambda_t + \sum_{k\geq h}\tau_{ck} + \beta X_{ct} + \nu_{ct}
    \end{equation*}
    with 
    \vspace{9pt}
    \begin{wideitemize}
        \item[\textcolor{fblu}{\textbullet}] \(\textcolor{fblu}{c}\): county, \(\textcolor{fblu}{t}\): time (year-month), \(\textcolor{fblu}{k = t - z_c}\): time difference from PDMP implementation year in county \(\textcolor{fblu}{c}\), \(\textcolor{fblu}{z_c}\)
        \item[\textcolor{fblu}{\textbullet}] \(\textcolor{fblu}{y_{ct}}\): labor market outcome; \(\textcolor{fblu}{X_{ct}}\): demographic covariates, sector shares and drug mortality; \(\textcolor{fblu}{\nu_{ct}}\): idiosyncratic shock 
    \end{wideitemize}
    \vspace{9pt}
    State-level changes must be exogenous at the county level for \textcolor{fblu}{identification} and no anticipation up to \(\textcolor{fblu}{h}\) periods

    \begin{center} % 
        %\includegraphics[scale=0.4]{mop10_lab_force_rate.png}
        \includegraphics[scale=0.4]{pmq10_lab_for_rate.png}
    \end{center}

    \hyperlink{perc_comparison_3}{\beamerbutton{Percentiles comparison}}
    \hyperlink{ta_3}{\beamerbutton{Time average}}
    \hyperlink{presc_3}{\beamerbutton{Prescriptions}}

@@

    \begin{center} %pmq10_unemp_rate.png
        %\includegraphics[scale=0.4]{mop10_unemp_rate.png}
        \includegraphics[scale=0.4]{pmq10_unemp_rate.png}
    \end{center}

    \hyperlink{perc_comparison_1}{\beamerbutton{Percentiles comparison}}
    \hyperlink{ta_1}{\beamerbutton{Time average}}
    \hyperlink{presc_1}{\beamerbutton{Prescriptions}}

@@

    \begin{center} % pmq10_emp_rate.png
        %\includegraphics[scale=0.4]{mop10_emp_rate.png}
        \includegraphics[scale=0.4]{pmq10_emp_rate.png}
    \end{center}

    \hyperlink{perc_comparison_2}{\beamerbutton{Percentiles comparison}}
    \hyperlink{ta_2}{\beamerbutton{Time average}}
    \hyperlink{presc_2}{\beamerbutton{Prescriptions}}

@@

    \label{heroin_result}
    \frametitle{Results} % Title
    \framesubtitle{}  % Subtitle
    \rmfamily % Font

    \begin{center} % pmq10_emp_rate.png
        %\includegraphics[scale=0.4]{mop10_emp_rate.png}
        \includegraphics[scale=0.4]{pmq10_heroin.png}
    \end{center}

    \hyperlink{table_heroin}{\beamerbutton{Coefficients}}

### 2024-06-10 slides/introduction.tex
before presentation

    \begin{wideitemize}
        \item Opioid misuse can lead the victims to negative Labor Market Outcomes (\textcolor{fblu}{LMOs})
        \item The impact of substance abuse on LMOs might be mediated by labor market regulations
        \item \textcolor{fblu}{Minimum wage rates} can affect this impact 
        \vspace{9pt}
        \begin{wideitemize}
            \item[\textcolor{fblu}{\textbullet}] Negatively, through their effect on \textcolor{fblu}{labor demand for low-skill jobs} 
            \item[\textcolor{fblu}{\textbullet}] Positively, if they address the reasons that cause \textcolor{fblu}{addiction} in the first place \(\to\) \textcolor{fblu}{Deaths of despair}
        \end{wideitemize}
        %\item The dominance of each effect depends on how \textcolor{fblu}{binding} minimum wage rates are across labor markets
        \item How \textcolor{fblu}{binding} minimum wage rates are across labor markets is the relevant measure
    \end{wideitemize}

@@

    \begin{wideitemize}
        \item More stringent regulations on opioid access can make the victims to 
        \vspace{9pt}
        \begin{wideitemize}
            \item[\textcolor{fblu}{\textbullet}] \textcolor{fblu}{Quit}, which might imply some disutility, or
            \item[\textcolor{fblu}{\textbullet}] \textcolor{fblu}{Switch to the black market}
        \end{wideitemize}
        \item This decision affects the MPL of the worker
        \item In this scenario, minimum wage rates might
        \vspace{9pt}
        %\begin{wideitemize}
        %    \item[\textcolor{fblu}{\textbullet}] Improve labor outcomes if better living conditions tackle the causes of addiction and relapsing (\(\textcolor{fblu}{w_{min}}\) \textcolor{fblu}{not binding})
        %    \item[\textcolor{fblu}{\textbullet}] Foster addiction, if quitting doesn't improve labor prospects because \(\textcolor{fblu}{w_{min}}\) \textcolor{fblu}{binding} 
        %\end{wideitemize}
        \begin{wideitemize}
            \item[\textcolor{fblu}{\textbullet}] Increase the rates of unemployment of the workers that don't quit (\(\textcolor{fblu}{w_{min}}\) \textcolor{fblu}{binding})
            \item[\textcolor{fblu}{\textbullet}] Not have an impact on employment rates for addicted workers (\(\textcolor{fblu}{w_{min}}\) \textcolor{fblu}{not binding})
        \end{wideitemize}
    \end{wideitemize}

@@

    \begin{equation*}
        \begin{aligned}
            w^{min}\,\,\text{not binding} & \xrightarrow[\text{passed}]{\text{Prescription law}}
            \begin{cases}
                \text{\textcolor{fblu}{Quit}} \\
                \text{LMOs improve} \\
                \downarrow \text{Prescription rates} \\
                \downarrow \text{Mortality} \\
            \end{cases} \\
            & \\
            w^{min}\,\,\text{binding} & \xrightarrow[\text{passed}]{\text{Prescription law}}
            \begin{cases}
                \text{\textcolor{fblu}{Black market}} \\
                \text{LMOs worsen} \\
                \downarrow \text{Prescription rates} \\
                \uparrow \text{Mortality} \\
            \end{cases} \\ 
        \end{aligned}
    \end{equation*}

@@

@@

    \begin{wideitemize}
        \item \textcolor{fgre}{Cengiz et al. (2019)} \(\to\) minimum wage changes reduced employment in low-wage jobs of tradeable sectors
        \item \textcolor{fgre}{Aliprantis, Fee, and Schweitzer (2023)} \(\to\) large and significant negative impact of prescription rates on labor force participation
        \item \textcolor{fgre}{Alpert, Powell, and Pacula (2018)} \(\to\) positive relation between OxyContin misuse and heroin deaths 
    \end{wideitemize}

>>>>

    \begin{wideitemize}
        \item Opioid misuse can lead the victims to negative Labor Market Outcomes (\textcolor{fblu}{LMOs})
        \item The impact of substance abuse on LMOs might be mediated by labor market regulations
        \item \textcolor{fblu}{Minimum wage rates} can affect this impact 
        \vspace{9pt}
        \begin{wideitemize}
            \item[\textcolor{fblu}{\textbullet}] Negatively, through their effect on \textcolor{fblu}{labor demand} for low-skill jobs %and job-searching behavior for low-skill jobs 
            \item[\textcolor{fblu}{\textbullet}] Positively, if they address the reasons that cause addiction in the first place \(\to\) \textcolor{fblu}{Deaths of despair}
        \end{wideitemize}
        %\item The dominance of each effect depends on how \textcolor{fblu}{binding} minimum wage rates are across labor markets
        \item How \textcolor{fblu}{binding} minimum wage rates are across labor markets is the relevant measure
    \end{wideitemize}

@@

    \begin{wideitemize}
        \item More stringent regulations on opioid access can make the victims of misuse to 
        \vspace{9pt}
        \begin{wideitemize}
            \item[\textcolor{fblu}{\textbullet}] \textcolor{fblu}{Quit}, which might imply some disutility, or
            \item[\textcolor{fblu}{\textbullet}] \textcolor{fblu}{Switch to the black market}
        \end{wideitemize}
        \item This decision affects the ability of the individual to participate in the labor market and find a job
        %\item Withdrawing, through its impact on the MPL of the victim, 
        \item Minimum wage rates might change the incentives of the victims
        \item If these are \textcolor{fblu}{binding}, and labor demand is affected, the benefits of quitting will be lower
        %\item If \(\textcolor{fblu}{w^{min}}\) is too binding, workers might be discouraged to quit opioids
        %\item Workers that face a more binding minimum wage in their labor markets might be discouraged to withdraw from opioids, as they would face a tougher job market search
    \end{wideitemize}

@@

    \begin{wideitemize}
        \item More stringent regulations on opioid access can make the victims to 
        \vspace{9pt}
        \begin{wideitemize}
            \item[\textcolor{fblu}{\textbullet}] \textcolor{fblu}{Quit}, which might imply some disutility, or
            \item[\textcolor{fblu}{\textbullet}] \textcolor{fblu}{Switch to the black market}
        \end{wideitemize}
        \item This decision affects the MPL of the worker
        \item In this scenario, minimum wage rates might
        \vspace{9pt}
        %\begin{wideitemize}
        %    \item[\textcolor{fblu}{\textbullet}] Increase the rates of unemployment of the workers that don't quit (\(\textcolor{fblu}{w^{min}}\) \textcolor{fblu}{binding})
        %    \item[\textcolor{fblu}{\textbullet}] Not have an impact on employment rates for addicted workers (\(\textcolor{fblu}{w^{min}}\) \textcolor{fblu}{not binding})
        %\end{wideitemize}
        \begin{wideitemize}
            \item[\textcolor{fblu}{\textbullet}] Increase the participation rates of the workers that quit (\(\textcolor{fblu}{w^{min}}\) \textcolor{fblu}{not binding})
            \item[\textcolor{fblu}{\textbullet}] Not have an impact on participation and employment rates for addicted workers (\(\textcolor{fblu}{w^{min}}\) \textcolor{fblu}{binding})
        \end{wideitemize}
    \end{wideitemize}

@@

    \frametitle{Incentives} % Title
    \framesubtitle{}  % Subtitle
    \rmfamily % Font

    \begin{wideitemize}
        \item If addicted individuals face a binding \(\textcolor{fblu}{w^{min}}\), they
        \vspace{9pt}
        \begin{wideitemize}
            \item[\textcolor{fblu}{\textbullet}] Might be discouraged to quit opioids (\textit{Cost of quitting} > \textit{Prospective labor earnings})
            \item[\textcolor{fblu}{\textbullet}] We shouldn't expect an increase in participation rates
            \item[\textcolor{fblu}{\textbullet}] Illegal opioid consumption should also be higher
        \end{wideitemize}
        \item But if \(\textcolor{fblu}{w^{min}}\) is not binding
        \vspace{9pt}
        \begin{wideitemize}
            \item[\textcolor{fblu}{\textbullet}] The incentives to quit opioids are higher
            \item[\textcolor{fblu}{\textbullet}] An increase in participation rates might follow
            \item[\textcolor{fblu}{\textbullet}] The impact on unemployment rates is less clear
        \end{wideitemize}
    \end{wideitemize}

    \frametitle{I find that} % Title
    \framesubtitle{}  % Subtitle
    \rmfamily % Font

    \begin{wideitemize}
        \item Policies aimed at stoping opioid misuse
        \vspace{9pt}
        \begin{wideitemize}
            \item[\textcolor{fblu}{\textbullet}] Increased participation rates only where \(\textcolor{fblu}{w^{min}}\) \textcolor{fblu}{was not binding}
            \item[\textcolor{fblu}{\textbullet}] The increase was short-lived, but the impact on unemployment rates was persistent
            \item[\textcolor{fblu}{\textbullet}] Their impact on prescription rates seem to be the main, but not the only, driver of these results
        \end{wideitemize}
        \item At the same time
        \vspace{9pt}
        \begin{wideitemize}
            \item[\textcolor{fblu}{\textbullet}] They had no labor market consequences where \(\textcolor{fblu}{w^{min}}\) \textcolor{fblu}{was binding}
            \item[\textcolor{fblu}{\textbullet}] Their impact on heroin and synthetic opioid deaths was increasing in \(\textcolor{fblu}{w^{min}}\) bindingness 
        \end{wideitemize}
    \end{wideitemize}

@@

    \begin{wideitemize}
        %\item Minimum wage changes reduced employment in low-wage jobs of tradeable sectors: \textcolor{fgre}{Cengiz et al. (2019)} 
        \item Large and significant negative impact of prescriptions and misuse on labor outcomes: {\footnotesize \textcolor{fgre}{Aliprantis, Fee, and Schweitzer (2023), Beheshti (2022), Greenwood, Guner and Kopecky (2022)}} % , Harris et al. (2018)
        \item Prescription drugs regulations can be effective in reducing opioid misuse: {\footnotesize  \textcolor{fgre}{Buchmueller and Carey (2018), Ukert and Polsky (2023)}}
        \item Positive relation between legal opioid misuse and heroin deaths: {\footnotesize \textcolor{fgre}{Alpert, Powell, and Pacula (2018), Cicero, Ellis, and Surratt (2012), Cicero and Ellis (2015)} }
    \end{wideitemize}

### 2024-06-10 slides/model.tex
before presentation

    An addicted worker faces
    \vspace{9pt}
    \begin{wideitemize}
        \item A health/performance \textcolor{fblu}{cost of opioid consumption} \(O_{it}\)
        \item This cost depends on \textcolor{fblu}{legal opioids consumption} \(l_{it}\) and \textcolor{fblu}{black market opioids consumption} \(h_{it}\) (say, heroin)
        \item Which opioid is consumed depends on the \textcolor{fblu}{availability of legal opioids} \(z_{it}\) (\(= 1\) if prescription law is in place)
        \item I assume that illegal opioids are more harmful than legal opioids 
        \[h_{it} = l_{it} + \mathcal{C}\]
    \end{wideitemize}

@@

    \label{decision_making}
    \frametitle{Policy and decision making} % Title
    \framesubtitle{}  % Subtitle
    \rmfamily % Font

    \begin{wideitemize}
        \item The \textcolor{fblu}{total cost of opioid consumption} is
        \[
        O_{it} = z_{t}\left(1-q_{it}\right)h_{it} + (1-z_{t})l_{it}
        \]
        where \(q_{it} = 1\) \textcolor{fblu}{if the worker quits opioids}
        \item The worker quits if

        \[
        q_{it} = \mathbbm{1}\{\text{Exp. utility of quitting} \geq \text{Disutility of quitting}\}
        \]

    \end{wideitemize}
    \hyperlink{quitting}{\beamerbutton{Quitting}}

@@

    \frametitle{Labor demand} % Title
    \framesubtitle{}  % Subtitle
    \rmfamily % Font

@@

    \begin{wideitemize}
        \item Assume for the moment that \textcolor{fblu}{the worker cannot quit opioids} and that \(l_{it} < o < h_{it}\)
        \item Then if the \textcolor{fblu}{minimum wage is binding} (\(w_{t} = w^{min}_t\)) and \textcolor{fblu}{the law is passed} (\(z_t = 1\))
        \[
        f(\theta_{it}) - \kappa < w^{min}_t \,\Rightarrow\, \text{unemployment}
        \]
        \vspace{-15pt}
        \item But if the \textcolor{fblu}{minimum wage is not binding} (\(w_{t} >> w^{min}_t\)) 
        \[
        f(\theta_{it}) - \kappa = w_t 
        \]
        \vspace{-15pt}
        \item What if the worker can quit opioids?
    \end{wideitemize}
    \hyperlink{quitting}{\beamerbutton{Quitting}} 
\end{frame}

>>>>

    An addicted individual faces
    \vspace{9pt}
    \begin{wideitemize}
        \item A health/performance \textcolor{fblu}{cost of opioid consumption} \(O_{it}\)
        \item This cost depends on \textcolor{fblu}{legal opioids consumption} \(l_{it}\) and \textcolor{fblu}{black market opioids consumption} \(h_{it}\) (say, heroin)
        \item Which opioid is consumed depends on the \textcolor{fblu}{availability of legal opioids} \(z_{t}\) (\(= 1\) if prescription law is in place)
        \item I assume that opioid misuse impedes the worker's ability to work
        %\item I assume that illegal opioids are more harmful than legal opioids 
        %\[h_{it} = l_{it} + \mathcal{C}\]
    \end{wideitemize}

@@

    \label{decision_making}
    \frametitle{Decision making} % Title
    \framesubtitle{}  % Subtitle
    \rmfamily % Font

    \begin{wideitemize}
        %\item The \textcolor{fblu}{total cost of opioid consumption} is
        \item The \textcolor{fblu}{decision rule of opioid consumption} is
        \[
        O_{it} = z_{t}\left(1-q_{it}\right)h_{it} + (1-z_{t})l_{it}
        \]
        where \(q_{it} = 1\) \textcolor{fblu}{if she quits opioids}
        \item The worker quits if

        \[
        q_{it} = \mathbbm{1}\{\text{Exp. utility of quitting} \geq \text{Disutility of quitting}\}
        \]
        \vspace{-15pt}
        \item Quitting and looking for a job are equivalent
    \end{wideitemize}
    %\hyperlink{quitting}{\beamerbutton{Quitting}}

\begin{comment}
\begin{frame}
2
    \frametitle{Labor demand} % Title
    \framesubtitle{}  % Subtitle
    \rmfamily % Font

\end{frame}
\end{comment}

    \frametitle{Labor market} % Title
    \framesubtitle{}  % Subtitle
    \rmfamily % Font

    \begin{wideitemize}
        \item The market has a \textcolor{fblu}{job finding rate} 
        \[
            p_{it} = m_{it}/u_{it} 
        \]
        where \(m_{it}\) is the \textcolor{fblu}{number of matches} and \(u_{it}\) is the \textcolor{fblu}{number of unemployed workers}

        \item Matches are an increasing function of vacancies \(v_{it}\)
        \[
            m_{it} = M(v_{it}, u_{it})
        \]
        where \(M\left(\cdot \right) \) is a matching function
        \item I assume that more vacancies are open where the minimum wage is less binding ({\footnotesize  \textcolor{fgre}{Flinn, 2010}})
    \end{wideitemize}

@@

    \frametitle{Quitting decision} % Title
    \framesubtitle{}  % Subtitle
    \rmfamily % Font

    \begin{wideitemize}
        \item It follows that
        \[
            p_{w_{it} > w^{min}_t} \geq p_{w_{it} = w^{min}_t}
        \]
        \vspace{-15pt}
        \item If \(\textcolor{fblu}{w^{min}_t}\) is not binding
        \[
            q_{w_{it} > w^{min}_t} = \mathbbm{1}\{p_{w_{it} > w^{min}_t}\cdot u(w_{it}L_{it}) \geq \mathcal{C}^{quit}\}
        \]
        \vspace{-15pt}
        \item Otherwise
        \[
            q_{w_{it} = w^{min}_t} = \mathbbm{1}\{p_{w_{it} = w^{min}_t}\cdot u(w^{min}_t L_{it}) \geq \mathcal{C}^{quit}\} 
        \]

    \end{wideitemize}

@@

    \begin{wideitemize}
        \item As long as
        \[
            p_{w_{it} > w^{min}_t}\cdot u(w_{it}L_{it}) > \mathcal{C}^{quit} > p_{w_{it} = w^{min}_t}\cdot u(w^{min}_t L_{it})
        \]
        we should see (after \(z_{t} = 1\))
        \vspace{9pt}
        \begin{wideitemize}
            \item[\textcolor{fblu}{\textbullet}] An increase in participation rates where the minimum wage is less binding (\(O_{it} = 0\))
            \item[\textcolor{fblu}{\textbullet}] An increase in illegal opioid consumption where the minimum wage is more binding (\(O_{it} = h_{it}\))
        \end{wideitemize}

    \end{wideitemize}

\begin{comment}
\begin{frame}

    \begin{wideitemize}
        \item Assume for the moment that \textcolor{fblu}{the worker cannot quit opioids} and that \(l_{it} < o < h_{it}\)
        \item Then if the \textcolor{fblu}{minimum wage is binding} (\(w_{t} = w^{min}_t\)) and \textcolor{fblu}{the law is passed} (\(z_t = 1\))
        \[
        f(\theta_{it}) - \kappa < w^{min}_t \,\Rightarrow\, \text{unemployment}
        \]
        \vspace{-15pt}
        \item But if the \textcolor{fblu}{minimum wage is not binding} (\(w_{t} >> w^{min}_t\)) 
        \[
        f(\theta_{it}) - \kappa = w_t 
        \]
        \vspace{-15pt}
        \item What if the worker can quit opioids?
    \end{wideitemize}
    \hyperlink{quitting}{\beamerbutton{Quitting}}

\end{frame}
\end{comment}
